Computing Restricted Isometry Constants via Mixed-Integer Semidefinite Programming

### 2016-03-23 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
paper: added biographies

>>>>

\begin{IEEEbiographynophoto}{Tristan Gally}
obtained a B.Sc. and an M.Sc. degree in mathematics with economics
from TU Darmstadt, Germany, in 2011 and 2013, respectively. Since
02/2014 he is a doctoral candidate at TU Darmstadt working as a
Researcher in the Collaborative Research Center 805, funded by the
German Research Foundation (DFG). His research interests are mainly
in mixed-integer semidefinite programming with applications in
compressed sensing and truss topology design.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Marc E. Pfetsch}
  obtained a Diploma degree in mathematics from the University of
  Heidelberg, Germany, in 1997. He received a PhD degree in
  mathematics in 2002 and the Habilitation degree in 2008 from TU
  Berlin, Germany. From 2008 to 2012 he was a Full Professor for
  Mathematical Optimization at TU Braunschweig, Germany. Since 04/2012
  he has been a Full Professor for Discrete Optimization at TU
  Darmstadt, Germany. His research interests are mostly in discrete
  optimization, in particular symmetry in integer programs, compressed
  sensing, and algorithms for mixed integer programs.
\end{IEEEbiographynophoto}
